NFC and burnout in teachers - A replication and extension study

### 2022-02-23 Manuscript/Manuscript.Rmd
corrected brackets in materials section

## Material
All questionnaires were used in their German form.
Burnout was assessed using the 21-item Maslach Burnout Inventory [MBI, @Buessing1992], with items such as "I don't really care what happens to some recipients" and responses on a 7-point Likert scale from 0 (never) to 6 (every day).
Its subscales *emotional exhaustion*, *depersonalization*, and *reduced personal efficacy* showed acceptable internal consistency (Cronbach’s $\alpha>.70$) and low retest reliabilities of $r_{tt}=.60$, $r_{tt}=.54$, and $r_{tt}=.57$, respectively, over the span of one year in teachers [@Maslach1997].
NFC was assessed with the 16-item short version of the German NFC scale [NCS; @Bless1994], consisting of items (e.g., "Thinking is not my idea of fun", recoded) that are answered on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
The scale shows comparably high internal consistency [Cronbach’s $\alpha>.80$; @Bless1994; @Fleischhauer2010] and a retest reliability of $r_{tt}=.83$ across 8 to 18 weeks [@Fleischhauer2015].
Self-control was measured using the short form of the German Self-Control Scale [SCS-K-D; @Bertrams2009a] that comprises 13 items (e.g., “I am able to work effectively toward long-term goals”) with a 5-point Likert scale ranging from -2 (completely disagree) to +2 (completely agree), with comparably high reliability [Cronbach’s $\alpha$  ~ .80, 7-week retest reliability $r_{tt}$  = .82; @Bertrams2009a].
Reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire [ERQ, @Abler2009].
The scale has items such as "When I’m faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (reappraisal) and "I keep my emotions to myself" (suppression), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach’s $\alpha>.75$) [@Preece2019].
Work satisfaction was assessed using the Allgemeine Arbeitszufriedenheit questionnaire [@Fischer2014] with items such as "Sometimes I feel like my work doesn't really matter in my firm", which are answered on a 5-point Likert scale from 1 to 5 and different anchors depending on the item.
The scale has a split-half reliability of $r_{tt}=.95$ [@Fischer2014].
Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently had a higher workload.
The translated Covid-19 items can be found in the *Supplementary Material S1*.
Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar [@BoehmKasper2001] could not be used, so we could not replicate the mediation of NFC and burnout by active and passive coping.

>>>>

## Material
All questionnaires were used in their German form.
Burnout was assessed using the 21-item Maslach Burnout Inventory [MBI, @Buessing1992], with items such as "I don't really care what happens to some recipients" and responses on a 7-point Likert scale from 0 (never) to 6 (every day).
Its subscales *emotional exhaustion*, *depersonalization*, and *reduced personal efficacy* showed acceptable internal consistency (Cronbach’s $\alpha>.70$) and low retest reliabilities of $r_{tt}=.60$, $r_{tt}=.54$, and $r_{tt}=.57$, respectively, over the span of one year in teachers [@Maslach1997].
NFC was assessed with the 16-item short version of the German NFC scale (NCS) [@Bless1994], consisting of items (e.g., "Thinking is not my idea of fun", recoded) that are answered on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
The scale shows comparably high internal consistency (Cronbach’s $\alpha>.80$) [@Bless1994; @Fleischhauer2010] and a retest reliability of $r_{tt}=.83$ across 8 to 18 weeks [@Fleischhauer2015].
Self-control was measured using the short form of the German Self-Control Scale [SCS-K-D; @Bertrams2009a] that comprises 13 items (e.g., “I am able to work effectively toward long-term goals”) with a 5-point Likert scale ranging from -2 (completely disagree) to +2 (completely agree), with comparably high reliability (Cronbach’s $\alpha>.80$, 7-week retest reliability $r_{tt}=.82$) [@Bertrams2009a].
Reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ) [@Abler2009].
The scale has items such as "When I’m faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (reappraisal) and "I keep my emotions to myself" (suppression), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach’s $\alpha>.75$) [@Preece2019].
Work satisfaction was assessed using the Allgemeine Arbeitszufriedenheit questionnaire [@Fischer2014] with items such as "Sometimes I feel like my work doesn't really matter in my firm", which are answered on a 5-point Likert scale from 1 to 5 and different anchors depending on the item.
The scale has a split-half reliability of $r_{tt}=.95$ [@Fischer2014].
Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently had a higher workload.
The translated Covid-19 items can be found in the *Supplementary Material S1*.
Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar [@BoehmKasper2001] could not be used, so we could not replicate the mediation of NFC and burnout by active and passive coping.
